\documentclass[aspectratio=169]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[spanish]{babel}

% Load our custom beamer style package
\usepackage{custombeamer}

\begin{document}

% ==============================================================================
% CATEGORY 1: TITLE SLIDES (PORTADAS)
% ==============================================================================

% Portada Estilo 1: Minimalist
\titleSlideMinimalist
  {Title (Style: Minimalist)} % Title
  {Subtitle / Presentation Description} % Subtitle
  {Author Name} % Author
  {Institution / Date} % Date/Institution

% Portada Estilo 2: Split Banner
\titleSlideSplit
  {Title (Style: Split Banner)} % Title
  {Subtitle / Presentation Description} % Subtitle
  {Author Name} % Author
  {Institution / Date} % Date/Institution

% Portada Estilo 3: Dark Mode
\titleSlideDarkMode
  {Title (Style: Dark Mode)} % Title
  {Subtitle / Presentation Description} % Subtitle
  {Author Name} % Author
  {Institution / Date} % Date/Institution


% ==============================================================================
% CATEGORY 2: TABLE OF CONTENTS / AGENDA
% ==============================================================================

% Agenda Estilo 1: Numbered Steps
\agendaSlideNumbered
  {Agenda Title (Style: Numbered Steps)}
  {Step 1: Description of first milestone}
  {Step 2: Description of second milestone}
  {Step 3: Description of third milestone}
  {Step 4: Description of fourth milestone}

% Agenda Estilo 2: Cards Grid
\agendaSlideCards
  {Agenda Title (Style: Cards Grid)}
  {Topic 1: Key topic overview}
  {Topic 2: Key topic overview}
  {Topic 3: Key topic overview}
  {Topic 4: Key topic overview}

% Agenda Estilo 3: Progress Tracker (Highlighting item 2)
\agendaSlideProgress
  {Agenda Title (Style: Progress Tracker)}
  {2} % Highlight item index (1-4)
  {Topic 1: Completed / Inactive}
  {Topic 2: Active / Highlighted}
  {Topic 3: Upcoming / Inactive}
  {Topic 4: Upcoming / Inactive}


% ==============================================================================
% CATEGORY 3: SECTION DIVIDERS (SECCIONES)
% ==============================================================================

% Sección Estilo 1: Solid Color
\sectionSlideSolid
  {01} % Section Number/Label
  {Section Title (Style: Solid Color)} % Section Title
  {Description of the topics covered in this section} % Subtitle

% Sección Estilo 2: Left Stripe
\sectionSlideStripe
  {02} % Section Number/Label
  {Section Title (Style: Left Stripe)} % Section Title
  {Description of the topics covered in this section} % Subtitle

% Sección Estilo 3: Dark Mode
\sectionSlideDark
  {03} % Section Number/Label
  {Section Title (Style: Dark Mode)} % Section Title
  {Description of the topics covered in this section} % Subtitle


% ==============================================================================
% CATEGORY 4: CONTENT SLIDES (CONTENIDO)
% ==============================================================================

% Contenido Estilo 1: Bullet Points & Card
\contentSlideBulletCard
  {Slide Title (Style: Bullet \& Card)}
  {
    \begin{itemize}
      \item \textbf{Point 1:} Description of a core fact or argument.
      \item \textbf{Point 2:} Another supporting detail about this slide.
      \item \textbf{Point 3:} Bullet lists look clean and have customized icons.
    \end{itemize}
  }
  {Takeaway Header}
  {This side card highlights a key statistic, quote, or critical takeaway that balances the list on the left.}

% Contenido Estilo 2: Two-Column Split
\contentSlideTwoCols
  {Slide Title (Style: Two-Column Split)}
  {Column 1 Header}
  {
    Detailed paragraph or list for the left column.
    \begin{itemize}
      \item Sub-point A.
      \item Sub-point B.
    \end{itemize}
  }
  {Column 2 Header}
  {
    Detailed paragraph or list for the right column. Useful for comparison or pros vs. cons.
    \begin{itemize}
      \item Sub-point C.
      \item Sub-point D.
    \end{itemize}
  }

% Contenido Estilo 3: Quote & Big Stat
\contentSlideQuoteStat
  {Slide Title (Style: Quote \& Big Stat)}
  {99.9\%} % Huge text/stat/keyword
  {Metric / Keyword Label} % Label below the metric
  {“A beautiful layout combined with a strong metric creates an unforgettable slide for your audience.”} % Takeaway text

\end{document}
